Working title: Highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2019-10-11 write_up/highlights.tex
Adding cover letter and highlights

\documentclass[12pt]{letter}
\usepackage[margin=2.54cm, a4paper]{geometry}
\signature{\vspace*{-1cm} 
	Paul Dolder \\ 
	Dr C\'oil\'in Minto\\ 
	Prof Jean-Marc Guarini \\
	Dr Jan Jaap Poos}
\address{Paul Dolder \\
	Marine and Freshwater Research Centre \\ 
	Galway-Mayo Institute of Technology \\ 
	Dublin Road \\ 
	Galway \\ 
	Ireland}

@@

\begin{letter}{Prof. Brian D. Fath \\ Department of Biological Sciences \\
		Towson University \\ 8000 York Road \\ Towson \\ Maryland 21252 \\ USA}
\opening{Dear Professor Fath,}

We would like to submit an \emph{Original research} paper titled \emph{`Highly
	resolved spatiotemporal simulations for exploring mixed fisheries
	dynamics'} for consideration in \emph{Ecological modelling}. In this
paper we develop and apply a simulation model of a ecological-fishery system
where individual fishing vessels exploit multiple heterogeneously distributed
fish stocks with full spatiotemporal population dynamics. In it we explore the
importance of spatial and temporal scale when modelling fishery interactions,
particularly in relation to modelling observational data from a system with
preferential sampling.\\

Our study tackles the issue of how fishers exploit a dynamic natural resource
with uncertain knowledge of its distribution. We detail how this affects our
understanding of the fisheries interactions with multiple fish populations,
which cannot be achieved with a conventional modelling approach. By capturing
dynamics observed in fisheries data in a novel simulation model where the
entire dynamics of the system (including the true spatial distribution of the
populations) are known, we expose that degrading the spatial and temporal
resolution of data through aggregation reduces our ability to define effective
spatial management measures. This would not of been possible without the highly
details and resolved simulation approach used here. The model has many
potential additional applications which we discuss, with the model made
available as an R software package for users to explore.\\

Should you consider our work suitable for review, we would like to suggest the
following associate editor and potential reviewers with a rationale below each:

\begin{itemize} 
	\item {\bf Associate Editor} Prof. Terrance Quinn II, College of
		Fisheries and Oceans, University of Fairbanks, Alaska
		(tjquinnii@alaska.edu).\\ 
	\item {\bf Reviewer} Dr David Peel, Commonwealth Scientific and
		Industrial Research Organisation (CSIRO), Castray Esplanade,
		Hobart TAS 7000, Australia (david.peel@csiro.au). \\
		Established expert in finite mixture modelling.  
	\item {\bf Reviewer} Dr John Morrengiello, University of Melbourne,
		Melbourne, Australia (john.morrongiello@unimelb.edu.au) \\
		Early career scientist with expertise in quantitative aquatic
		ecology and evolution along with publications on growth
		modelling.  
	\item {\bf Reviewer} Dr Ken Newman, U.S. Fish and Wildlife Service,
		Lodi Fish and Wildlife Office, 850 Guild Avenue, Lodi, CA
		95240, USA (Ken\_Newman@fws.gov)\\ Established expert in
		mathematical and applied statistics with application to natural
		resource management.  
\end{itemize}

Thank you for your time and consideration.

\closing{Yours Sincerely,} \end{letter}

>>>>

\documentclass{article}

@@

\begin{itemize}

	\item one
	\item two
	\item three
	\item four
	\item five 
	\item six

\end{itemize}

### 2019-10-11 write_up/mixfishsim_ecolmod.tex
Adding cover letter and highlights

%% Group authors per affiliation:
\author[1,2]{Paul J. Dolder\corref{c}}
\cortext[c]{Corresponding author}
\ead{paul.dolder@gmit.ie}

@@

\begin{keyword}
Some\sep keywords \sep here. Max 6 
\MSC[2010] 00-01\sep  99-00
\end{keyword}

@@

\section*{Funding} This work was supported by the MARES doctoral training
program (MARES\_14\_15) and the Centre for Environment, Fisheries and
Aquaculture Science seedcorn program (DP227AC).

@@

\begin{figure}[!ht]
	\includegraphics[width=\linewidth]{../analysis/Data_Aggregation_space_Rev2}
	\caption{Data aggregation at different spatial resolutions over a
		ten year period.}
	\label{fig:1}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=\linewidth]{../analysis/Data_Aggregation_time_Rev2}
	\caption{Proportion of each population (y axis) for data aggregated at
		different temporal resolutions. Data is aggregated over a
		ten-year period for an area 20 x 20. Each bar represents either
		a week, month or year respectively.}
	\label{fig:2}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../analysis/F_trendsREV}
	\caption{Comparison of closure scenarios effect on fishing mortality
		trends. Line colour denotes timescale, while linestyle
		denotes spatial resolution. The vertical dashed line
		indicates the onset of the spatial closures.}
	\label{fig:3}
\end{figure}

@@

\begin{figure}[!ht]
	\centering
	\includegraphics[width =\linewidth]{./Plots/Closure_effectiveness_CF}
	\caption{Effectiveness of closure with regards to reducing fishing
		mortality on protected population (further left on x-axis is
		best) and maintaining high catches in the fishery (highest on
		y-axis is best). The numbers indicate the spatial resolution of
		the data, while grey lines indicate the direction of the
		trade-off between reducing fishing mortality and overall
		catches.}
	\label{fig:ce}
\end{figure}

>>>>

%% Group authors per affiliation:
\author[1,2]{Paul J. Dolder\corref{c}}
\cortext[c]{Corresponding author}
\ead{paul.dolder@research.gmit.ie}

@@

\begin{keyword}
spatiotemporal \sep mixed fisheries \sep individual based \sep spatial
management \sep homogeneity \sep  preferential sampling
\MSC[2010] 00-01\sep  99-00
\end{keyword}

@@

\section*{Funding} This work was supported by the MARES doctoral training
program (MARES\_14\_15) and the Centre for Environment, Fisheries and
Aquaculture Science seedcorn program (DP227AC). The authors declare no
competing interests.

\section*{CRediT author statement} \textbf{Paul Dolder:} Conceptualisation,
methodology, software, writing - original draft. \textbf{Cóilín Minto:}
Conceptualisation, Methodology, writing - review and editing, supervision,
funding acquisition. textbf{Jean-Marc Guarini:} methodology, writing - review
and editing, funding acquisition, supervision. \textbf{Jan Jaap Poos:}
methodology, writing - review and editing, supervision. \

@@

\begin{figure}[!ht]
	\includegraphics[width=\linewidth]{../analysis/Data_Aggregation_space_Rev2}
	\caption{[Colour] Data aggregation at different spatial resolutions over a
		ten year period.}
	\label{fig:1}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=\linewidth]{../analysis/Data_Aggregation_time_Rev2}
	\caption{[Colour]Proportion of each population (y axis) for data aggregated at
		different temporal resolutions. Data is aggregated over a
		ten-year period for an area 20 x 20. Each bar represents either
		a week, month or year respectively.}
	\label{fig:2}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../analysis/F_trendsREV}
	\caption{[Colour]Comparison of closure scenarios effect on fishing mortality
		trends. Line colour denotes timescale, while linestyle
		denotes spatial resolution. The vertical dashed line
		indicates the onset of the spatial closures.}
	\label{fig:3}
\end{figure}

@@

\begin{figure}[!ht]
	\centering
	\includegraphics[width =\linewidth]{./Plots/Closure_effectiveness_CF}
	\caption{[Colour]Effectiveness of closure with regards to reducing fishing
		mortality on protected population (further left on x-axis is
		best) and maintaining high catches in the fishery (highest on
		y-axis is best). The numbers indicate the spatial resolution of
		the data, while grey lines indicate the direction of the
		trade-off between reducing fishing mortality and overall
		catches.}
	\label{fig:ce}
\end{figure}
